---
title: "marshallproj"
author: "PhiPrime"
date: "8/17/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

This file is created to briefly explore data from **[The Marshall Project on incarcerated people's political views]()**  
```{r message = FALSE}
url <- "https://raw.githubusercontent.com/themarshallproject/incarcerated_survey/master/data/incarcerated_survey_responses-marshallproject_slate-march_2019.csv"
fileLoc <- "./Data/marshall.csv"
download.file(url, fileLoc, method = "curl")
dat <- read.csv(fileLoc)
```
The following list is the variable names of the data  
```{r}
names(dat)
```
A lot of these variables seem to possibly be either discrete or continuous so we'll now look at the unique responses for each variable.  
```{r}
sapply(dat, unique)
```

It can be seen above that most of these variables are discrete factors. This would not prove too difficult to clean, with the exception of `how_get_news` (column 12), which would require some processing to make multiple new logical variables.  

For now we'll convert these variables to factors with the exception of `how_get_news` and the identities  
```{r}
fdat <- dat
fdat[sapply(fdat, is.character)] <- 
  lapply(fdat[sapply(fdat, is.character)], as.factor)
```

We'll now look at the summary of each of these catagories. Since the conversion to factor was quick, the logical questions are summarized as a numeric column. The percent that elected "yes" is represented by the mean in these cases.  
```{r}
summary(fdat)
```
The difference in TRUE/FALSE for Male or Female would require further investigation for the discrepency which would be explored should this data set be selected.

## Conclusion  
This data would require a bit of cleaning but nothing too complex. This is a viable source for the project.  






